---
title: "Identification of Gene Moldules In Larvae Brain Progenitors"
output: html_notebook
---

```{r Load Required libraries}
library(Seurat)
library(WGCNA)
library(hdWGCNA)
library(tidyverse)
library(UCell)
library(cowplot)
library(patchwork)
library(qlcMatrix)
library(igraph)
library(ggplot2)
library(corrplot)
library(MetBrewer)
```

```{r using the cowplot theme for ggplot}
#Using the cowplot theme for ggplot
theme_set(theme_cowplot())
```

```{r set random seed for reproducibility}
#Set random seed for reproducibility
set.seed(12345)
```

```{r optionally enable multithreading}
#Optionally enable multithreading
enableWGCNAThreads(nThreads = 8)
```

```{r Load Seurat Object}
#Load Seurat Object
larave.intigrated <- readRDS("larval.integrated.rds")
```

```{r Set Default Assay to integrated}
#Set Default Assay to integrated
DefaultAssay(larave.intigrated) <- "integrated"
```

```{r Scale data }
larave.intigrated <- ScaleData(larave.intigrated, verbose = FALSE)
```

```{r Run PCA}
#Run PCA
larave.intigrated <- RunPCA(larave.intigrated, npcs = 30, verbose = FALSE)
```

```{r Run non-linear dimentional reduction UMAP}
#Run non-linear dimentional reduction UMAP
larave.intigrated <- RunUMAP(larave.intigrated, reduction = "pca", dims = 1:30)
```

```{r Find neighbors}
#Find neighbors
larave.intigrated <- FindNeighbors(larave.intigrated, reduction = "pca", dims = 1:30)
```

```{r Find Clusters}
#Find Clusters
larave.intigrated <- FindClusters(larave.intigrated, resolution = 0.05)
```

```{r Cell type annotation}
#Cell type annotation
cell.type <-     c('0'	='progenitor',
                   '1'	='Differentiating progenitor',
                   '2'	='progenitor',
                   '3'	='progenitor',
                   '4'	='progenitor',
                   '5'	='progenitor',
                   '6'	='progenitor',
                   '7'	='progenitor'
)
```

```{r Set back default assay to RNA}
#Set back default assay to RNA
DefaultAssay(larave.intigrated) <- "RNA"
```

```{r Get variable genes in the integrated seurat object}
#Get variable genes in the integrated seurat object
var.features <- larave.intigrated@assays$integrated@var.features
```

```{r}
#Set up Seurat object for WGCNA analysis
larave.intigrated <- SetupForWGCNA(larave.intigrated, 
                                   features = var.features, 
                                   wgcna_name = "intermediate.progenitor")
```

I generate the metacell using the following parameters. I specify the "cluster.names" in the seurat metadata as the parameter to group.by and ident.group parameter. Additionally, maximum number of shared cells between two metacells kept as 10 in the mas_shared parameter together with 25 nearest neighbors, the parameter k. 

```{r}
#Construct metacells  in each group
larave.intigrated <- MetacellsByGroups(
  seurat_obj = larave.intigrated,
  group.by = "cluster.names",
  reduction = 'pca',
  k = 25, 
  max_shared = 10, 
  ident.group = 
)
```

```{r}
#Normalize metacell expression matrix
larave.intigrated <- NormalizeMetacells(larave.intigrated)
```

```{r}
#Set up the expression matrix
#I used the name of the group of interest in the group.by column
#I used RNA assay
#I used data slot for the normalized data 
larave.intigrated <- SetDatExpr(
  larave.intigrated,
  group_name = "progenitor", 
  group.by="cluster.names", 
  assay = 'RNA', 
  slot = 'data' 
)
```

```{r}
#Test different soft powers:
larave.intigrated <- TestSoftPowers(
  larave.intigrated,
  networkType = 'signed' 
)
```

```{r}
#Plot the results:
plot_list <- PlotSoftPowers(larave.intigrated)
```

```{r}
#Assemble with patchwork
wrap_plots(plot_list, ncol=2)
```

```{r}
# construct co-expression network:
larave.intigrated <- ConstructNetwork(
  larave.intigrated, soft_power=6,
  setDatExpr=FALSE,
  tom_name = 'Larvae.progenitor',
  overwrite_tom = TRUE
)
```

```{r}
#Generate dendrogram
larvae.dendrogram <- PlotDendrogram(larave.intigrated, main='Progenitor Dendrogram')
```

I am panning to change the default module colors in the dendrogram.

```{r}
#Get a table of just the module and it's unique color
mod_color_df <- GetModules(larave.intigrated) %>%
                           dplyr::select(c(module, color)) %>%
                           distinct %>% arrange(module)
```

```{r}
# The number of unique modules (subtract 1 because the grey module stays grey):
n_mods <- nrow(mod_color_df) - 1
```

```{r}
#Using the "Signac" palette from metbrewer, selecting for the number of modules
new_colors <- paste0(met.brewer("Signac", n=n_mods))
```

```{r}
#Reset the module colors
larave.intigrated <- ResetModuleColors(larave.intigrated, new_colors)
```

```{r}
#Re-run plotDendrogramfunction
new.larvae.dendrogram <- PlotDendrogram(larave.intigrated , main='Recolored Dendrogram')
```

```{r}
#Get topoligcal overlap matrix
TOM <- GetTOM(larave.intigrated)
```

```{r}
#Need to run ScaleData first or else harmony throws an error:
larave.intigrated <- ScaleData(larave.intigrated, features=var.features)
```

```{r}
# compute all MEs in the full single-cell dataset
larave.intigrated  <- ModuleEigengenes(larave.intigrated,group.by.vars= "cluster.names")
```

```{r}
#Harmonized module eigengenes:
hMEs <- GetMEs(larave.intigrated)
```

```{r}
#Get module eigengenes:
MEs <- GetMEs(larave.intigrated, harmonized=FALSE)
```

```{r}
#Compute eigengene-based connectivity (kME):
larave.intigrated <- ModuleConnectivity(larave.intigrated,
                                        group.by = 'cluster.names', 
                                        group_name = 'progenitor'
                                        )
```

```{r}
#Rename the modules
larave.intigrated <- ResetModuleNames(larave.intigrated, new_name = "Module_")
```

```{r}
#Plot genes ranked by kME for each module
pKME <- PlotKMEs(larave.intigrated, text_size = 4, ncol=5)
pKME+ plot_layout(ncol = 4)
```

```{r}
#Get the module assignment table:
modules.table <- GetModules(larave.intigrated)
modules.table <- modules.table %>% arrange(color) 
write.csv(modules.table, file = "larvae.module.gene.list.new.module.color.csv")
```

```{r}
#Get hub genes
hub_df <- GetHubGenes(larave.intigrated, n_hubs = 10)
write.csv(hub_df, file= "larave.hub.genes.csv")
```

```{r}
#Compute gene scoring for the top 25 hub genes by kME for each module with Seurat method
larave.intigrated <- ModuleExprScore(larave.intigrated,
                                     n_genes = 25,
                                     method='Seurat'
                                    )
```

```{r}
#Make a featureplot of hMEs for each module
plot_list <- ModuleFeaturePlot(
  larave.intigrated ,
  features='hMEs', # plot the hMEs
  order=TRUE # order so the points with highest hMEs are on top
)
# stitch together with patchwork
wrap_plots(plot_list, ncol=4)
```

```{r}
#Plot module correlagram
module.corr <- ModuleCorrelogram(larave.intigrated)
```

```{r}
#Get module network
mPlot <- ModuleNetworkPlot(larave.intigrated)
mPlot
```

```{r}
#Hubgene network
HubGeneNetworkPlot(
  larave.intigrated,
  n_hubs = 6, n_other=3,
  edge_prop = 1,
  mods = 'Module_1',
  edge.alpha = 0.5,
  vertex.label.cex = 1,
  hub.vertex.size = 4,
  other.vertex.size = 4,
)
```
 
